Palomar 5 Gaps

### 2024-10-28 paper/main.tex
compiled without draft mde
eqeq typo

      While Fig.\ref{fig:impact_geometry_statistics} demonstrates that mass, relative velocity, or impact parameter alone (from Eq.\ref{eqeq:change_in_momentum}) cannot predict gap formation, one interesting result emerges: no gaps are created from interactions with impact parameters greater than 200~pc. The stream widths are roughly 200~pc, with a radial thickness of about 100~pc. This finding is even more evident when examining the $b$-$M$ plane. A series of perturbers at roughly $\sim7 \times 10^5 M_\odot$ highlights NGC~2808's flybys, where all encounters with impact parameters under 200~pc result in gaps, while those beyond this distance do not.

>>>>

      While Fig.\ref{fig:impact_geometry_statistics} demonstrates that mass, relative velocity, or impact parameter alone (from Eq.\ref{eq:change_in_momentum}) cannot predict gap formation, one interesting result emerges: no gaps are created from interactions with impact parameters greater than 200~pc. The stream widths are roughly 200~pc, with a radial thickness of about 100~pc. This finding is even more evident when examining the $b$-$M$ plane. A series of perturbers at roughly $\sim7 \times 10^5 M_\odot$ highlights NGC~2808's flybys, where all encounters with impact parameters under 200~pc result in gaps, while those beyond this distance do not.
